Analytic Doppler Imaging

### 2019-08-19 tex/ms.tex
twospec working beautifully

\subsection{Limb darkening}
\label{sec:ld}
Thus far we have avoided mention of limb darkening, whose effect
on the observed spectrum can often be significant. A proper treatment of
limb darkening requires solution of radiative transfer equations and
should account for the temperature and composition gradients in the
stellar atmosphere. However, in the spirit of data-driven inference, we 
may simply weight the spatial component of our map by the limb darkening
profile of the star, which can either be imposed or learned from the data.

>>>>

\subsection{Limb darkening}
\label{sec:ld}
Thus far we have avoided mention of limb darkening, whose effect
on the observed spectrum can often be significant. A proper treatment of
limb darkening requires solution of radiative transfer equations and
should account for the temperature and composition gradients in the
stellar atmosphere. However, in the spirit of data-driven inference, we 
can approximate the effect of limb darkening by weighting the spatial
component of our map by the limb darkening profile of the star, which can 
either be imposed or learned from the data.
